Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
minor edits
minor correction
minor edit
minor correction for result section

 From Eq.~\eqref{eq:MRA-Wavelettransform} the level of approximation, $j$, can be determined. This way we choose wavelets upto level $j$ which can fully describe the spatial frequency contents of the underlying dynamics estimated from the observed field.}

@@

	w(r-r')=200\times N_{4;1,-3}(r-r')-100\times N_{4;0,-3}(r-r').

@@

@@

For each of the experiments, the estimation was applied to the final 900~ms, allowing the forward model's dynamics to stabilize from the initial conditions. The initial state, parameters and the support of the connectivity kernel were unknown to the estimator. The observation noise was set to $\boldsymbol\Sigma_{\varepsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\eta(r-r') = \varphi_{3,-2}(r-r')$ (B-spline, $j=3$).  The firing rate slope, $\varsigma$ was set to $0.56~mV^{-1}$ \citep{Wendling2005}. The observation kernel was modeled using a B-spline function, with a width of 0.08~mm at half the maximum amplitude where the distance between adjacent sensors was $0.05$~mm, resulting into $n_y = 161$ observations. The choice of B-spline function to model the observation kernel is justified by the experiment performed in \citep{Freestone2011}. The spacing and bandwidth of the sensors allowed the full spatial bandwidth of the field to be observed.  With this number of observations, the estimation problem was well-posed, i.e. the number of states, $n_x < n_y$ at each level of the decomposition. This is because the scaling functions are orthogonal to the wavelets at the same and higher levels of decomposition, and  the wavelets are orthogonal to each other across different scales (see Eqs.~\eqref{eq:MRA-PsiPsiOrthogonality} and \eqref{eq:MRA-PhiPsiOrthogonality}).

>>>>

 From Eq.~\eqref{eq:MRA-Wavelettransform} the frequency response of the wavelets and hence the level of approximation, $j$, can be determined. This way we choose wavelets upto level $j$ which can fully describe the spatial frequency contents of the underlying dynamics estimated from the observed field.}

@@

	w(r-r')=\theta_1\times N_{4;1,2}(r-r')+\theta_2\times N_{4;0,2}(r-r'),

@@

with $\theta_1=200$ and $\theta_2=-100$.

@@

For each of the experiments, the estimation was applied to the final 900~ms, allowing the forward model's dynamics to stabilize from the initial conditions. The initial state, parameters and the support of the connectivity kernel were unknown to the estimator. The observation noise was set to $\boldsymbol\Sigma_{\varepsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance function was set to $\eta(r-r') = \sigma_d\times\varphi_{4;3,2}(r-r')$ (B-spline, $j=3$) with $\sigma_d=0.53$.  The firing rate slope, $\varsigma$ was set to $0.56~mV^{-1}$ \citep{Wendling2005}. The observation kernel was modeled using a B-spline function, with a width of 0.08~mm at half the maximum amplitude where the distance between adjacent sensors was $0.05$~mm, resulting into $n_y = 161$ observations. The choice of B-spline function to model the observation kernel is justified by the experiment performed in \citep{Freestone2011}. The spacing and bandwidth of the sensors allowed the full spatial bandwidth of the field to be observed.  With this number of observations, the estimation problem was well-posed, i.e. the number of states, $n_x < n_y$ at each level of the decomposition. This is because the scaling functions are orthogonal to the wavelets at the same and higher levels of decomposition, and  the wavelets are orthogonal to each other across different scales (see Eqs.~\eqref{eq:MRA-PsiPsiOrthogonality} and \eqref{eq:MRA-PhiPsiOrthogonality}).
